\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
\author{Hao Peng}
\title{Grading}
\begin{document}
\maketitle
\begin{enumerate}
\item 50 points for homework question 1:
\begin{itemize}
\item Three renewal events: failure renewal; inspection renewal without replacement; inspection renewal with replacement. The probabilities of renewal events: $Pr(X+H<\tau)$,failure renewal; $Pr(X>\tau)$,inspection renewal without replacement; $Pr(X<\tau \cap X+H>\tau)$, inspection renewal with replacement. (10 points)
\item Substitute the pdf and cdf of $X$ (exponential distribution) and $H$ (uniform distribution) in the expressions for calculating the probabilities of renewal events. (10 points) A remark should be provided to consider the boundaries of the uniform distribution. Or, different cases have been distinguished to discuss the expressions considering the boundaries of the uniform distribution. (10 points)
\item Renewal cycle cost for different renewal events are correct. (10 points)
\item Renewal cycle length for different renewal events are correct. (10 points)  
\item If the closed forms of the integrals are derived, they will get extra 10 points (However, if they have 100 points for this homework, they can not get the extra points. In other words, the highest score for this assignment is 100 points).
\end{itemize}
\item 50 points for homework question 2:
\begin{itemize}
\item Two renewal events: failure renewal and inspection renewal. The probabilities of renewal events are correct. The summation of the probabilities of renewal events is one. (10 points)
\item Renewal cycle cost for different renewal events are correct. (10 points)
\item Renewal cycle length for different renewal events are correct. (10 points) 
\item The distribution of first passage time Tc is correct. (10 points)
\item The conditional first passage time Th given that Tc=u is correct. (10 points)

\end{itemize}
\end{enumerate}
\end{document}